---
title: "Vaccine Uptake in CYP"
output: html_document
df_print: tibble
---

```{r include=FALSE}
library(rmarkdown)
library(readr)
library(table1)
library(labelled)
library(knitr)
library(kableExtra)

source("00_Functions.R")

z_df = df
z_df_vulnerable = df_vulnerable

process_uptake_df = function(z_df) {
  # Label the various columns for the table 1 package
  # so they look nice
  z_df = z_df %>% mutate(Value = TRUE)
  label(z_df$simd2020_sc_quintile) = "SIMD2020 Quintile"
  label(z_df$age_range_group) = "Age"
  label(z_df$age_gp) = "Age"
  label(z_df$vacc_type) = "1st Dose Type"
  label(z_df$vacc_type_2) = "2nd Dose Type"
  return(z_df)
}

z_df = process_uptake_df(z_df)
z_df_vulnerable = process_uptake_df(z_df_vulnerable)

z_df = z_df %>% mutate(vacc_1_dose = factor(is.na(z_df$date_vacc_1), labels=c("Vaccinated", "Unvaccinated")))
z_df = z_df %>% mutate(vacc_2_dose = factor(is.na(z_df$date_vacc_2), labels=c("Vaccinated", "Unvaccinated")))
z_df = z_df %>% mutate(vacc_3_dose = factor(is.na(z_df$date_vacc_3), labels=c("Vaccinated", "Unvaccinated")))
label(z_df$vacc_1_dose) = "1st Dose"
label(z_df$vacc_2_dose) = "2nd Dose"
label(z_df$vacc_3_dose) = "3rd Dose"

# Everyone in the vulnerable cohort by definiton has a first dose,
# but process their second and third doses
z_df_vulnerable = z_df_vulnerable %>% mutate(vacc_1_dose = TRUE) %>% mutate(vacc_1_dose = factor(vacc_1_dose, labels = c("Vaccinated")))
z_df_vulnerable = z_df_vulnerable %>% mutate(vacc_2_dose = factor(is.na(z_df_vulnerable$date_vacc_2), labels=c("Vaccinated", "Unvaccinated")))
z_df_vulnerable = z_df_vulnerable %>% mutate(vacc_3_dose = factor(is.na(z_df_vulnerable$date_vacc_3), labels=c("Vaccinated", "Unvaccinated")))
```
## Characteristics of entire cohort
```{r, paged.print=FALSE, message=FALSE, warning=FALSE}
print(summary_factorlist_wt(z_df, "Value", c("Sex", "simd2020_sc_quintile","age_range_group", "vacc_1_dose", "vacc_2_dose", "vacc_3_dose", "vacc_type", "vacc_type_2", "age_at_vacc_1")), n=1000)
```



## Doses by age group
### 16 and 17 year olds
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
z_df_age_group = z_df %>% filter(age_range_group == "16 - 17") %>% mutate(age_gp = droplevels(age_gp)) 
z_df_age_group$t_vacc_1 = z_df_age_group$date_vacc_1 - a_begin_16_17
z_df_age_group$t_vacc_2 = z_df_age_group$date_vacc_2 - a_begin_16_17
z_df_age_group$t_vacc_3 = z_df_age_group$date_vacc_3 - a_begin_16_17

first_doses_given = z_df_age_group %>% 
                 dplyr::count(t_vacc_1, wt = eave_weight) %>% mutate(Count = cumsum(n)/nrow(z_df_age_group)) 
second_doses_given = z_df_age_group %>% 
                 dplyr::count(t_vacc_2, wt = eave_weight) %>% mutate(Count = cumsum(n)/nrow(z_df_age_group)) 
third_doses_given = z_df_age_group %>% 
                 dplyr::count(t_vacc_3, wt = eave_weight) %>% mutate(Count = cumsum(n)/nrow(z_df_age_group))

# This ensures we keep those vaccinated before the start of the vaccination program while 
# not showing them on the timeline
first_doses_given = first_doses_given %>% mutate(date_vacc_1 = t_vacc_1 + a_begin_16_17) %>%
  filter(date_vacc_1 >= a_begin_16_17)
second_doses_given = second_doses_given %>% mutate(date_vacc_2 = t_vacc_2 + a_begin_16_17) %>%
  filter(date_vacc_2 >= a_begin_16_17)
#third_doses_given = third_doses_given %>% mutate(date_vacc_3 = t_vacc_3 + a_begin_16_17) %>%
#  filter(date_vacc_3 >= a_begin_16_17)

#plot(first_doses_given$date_vacc_1 ,first_doses_given$Count *100, axes = FALSE, xlab = "Month and Year", ylab = "Vaccine Coverage", col='blue', ylim=c(0, 100), xlim=c(a_begin_16_17, a_end))
#points(second_doses_given$date_vacc_2,second_doses_given$Count * 100, xlab = "Month and Year", ylab = "Vaccine Coverage", col='red')
#axis(2, at = c(0, 20, 40, 60, 80, 100), labels = c("0%", "20%", "40%", "60%", "80%", "100%"))
#axis(1, at = as.Date(c("2021-08-01", "2021-09-01", "2021-10-01", "2021-11-01", "2021-12-01", "2022-01-01", "2022-02-01", "2022-03-01")), labels = c("Aug", "Sept", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar"))
g = ggplot() + geom_line(first_doses_given, mapping=aes(x=date_vacc_1, y=Count*100, colour="1st Dose")) +
  geom_line(second_doses_given, mapping=aes(x=date_vacc_2, y=Count*100, colour="2nd Dose")) +   scale_colour_manual("Age: 16 - 17 Years", 
                      breaks = c("1st Dose", "2nd Dose"),
                      values = c("blue", "red")) +
  scale_x_date(breaks="1 month", date_labels="%b %Y") + xlab("Date") + ylim(0, 100) + ylab("Vaccine Coverage (%)") +
  xlab("Month and Year") + theme_bw() + theme(legend.position = c(0.8, 0.9)) + geom_segment(aes(x = as.Date("2021-08-06"), y = 55, xend = as.Date("2021-08-06"), yend = 0), arrow = arrow(length = unit(0.3, "cm"))) +
  annotate("text", x = as.Date("2021-09-01"), y = 65, 
label="1st dose introduced on
6 August 2021
2nd dose - 12 weeks later")

print(g)
ggsave("figure1a.svg", g)
#points(third_doses_given$date_vacc_3,third_doses_given$Count, xlab = "Time", ylab = "Number of Doses", col='green')
```

### 12 to 15 year olds
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
z_df_age_group = z_df %>% filter(age_range_group == "12 - 15") %>% mutate(age_gp = droplevels(age_gp))
z_df_age_group$t_vacc_1 = z_df_age_group$date_vacc_1 - a_begin_12_15
z_df_age_group$t_vacc_2 = z_df_age_group$date_vacc_2 - a_begin_12_15
z_df_age_group$t_vacc_3 = z_df_age_group$date_vacc_3 - a_begin_12_15

# Remove any vaccinations given before the start date, but keep any unvaccinated people
#z_df_age_group = z_df_age_group %>% filter(is.na(t_vacc_1) | t_vacc_1 > 0)

first_doses_given = z_df_age_group %>% dplyr::count(t_vacc_1, wt = eave_weight) %>% mutate(Count = cumsum(n)/nrow(z_df_age_group))
second_doses_given = z_df_age_group %>% dplyr::count(t_vacc_2, wt = eave_weight) %>% mutate(Count = cumsum(n)/nrow(z_df_age_group))
#third_doses_given = z_df_age_group %>% dplyr::count(t_vacc_3, wt = eave_weight) %>% mutate(Count = cumsum(n)/nrow(z_df_age_group))

# This ensures we keep those vaccinated before the start of the vaccination program while 
# not showing them on the timeline
first_doses_given = first_doses_given %>% mutate(date_vacc_1 = t_vacc_1 + a_begin_12_15) %>%
  filter(date_vacc_1 >= a_begin_16_17)
second_doses_given = second_doses_given %>% mutate(date_vacc_2 = t_vacc_2 + a_begin_12_15)  %>%
  filter(date_vacc_2 >= a_begin_16_17)
#third_doses_given = third_doses_given %>% mutate(date_vacc_3 = t_vacc_3 + a_begin_12_15)  %>%
#  filter(date_vacc_3 >= a_begin_16_17)
 
g = ggplot() + geom_line(first_doses_given, mapping=aes(x=date_vacc_1, y=Count*100, color="1st Dose")) +
  geom_line(second_doses_given, mapping=aes(x=date_vacc_2, y=Count*100, color="2nd Dose")) +
  scale_colour_manual("Age: 12 - 15 Years", 
                      breaks = c("1st Dose", "2nd Dose"),
                      values = c("blue", "red")) +
  scale_x_date(breaks="1 month", date_labels="%b %Y") + xlab("Date") + ylim(0, 100) + ylab("Vaccine Coverage (%)") +
  xlab("Month and Year") + theme_bw() + theme(legend.position = c(0.8, 0.9)) + geom_segment(aes(x = as.Date("2021-09-20"), y = 55, xend = as.Date("2021-09-20"), yend = 0), arrow = arrow(length = unit(0.3, "cm"))) +   annotate("text", x = as.Date("2021-10-05"), y = 65, 
label="1st dose introduced on
20 September 2021
2nd dose - 12 weeks later")

#plot(first_doses_given$date_vacc_1,first_doses_given$Count *100, axes=FALSE, xlab = "Month and Year", ylab = "Vaccine Coverage", col='blue', ylim=c(0, 100), xlim=c(a_begin_16_17, a_end))
#points(second_doses_given$date_vacc_2, second_doses_given$Count * 100, xlab = "Month and Year", ylab = "Vaccine Coverage", col='red')
#points(third_doses_given$date_vacc_3, third_doses_given$Count, xlab = "Time", ylab = "Number of Doses", col='green')

#axis(2, at = c(0, 20, 40, 60, 80, 100), labels = c("0%", "20%", "40%", "60%", "80%", "100%"))
#axis(1, at = as.Date(c("2021-08-01", "2021-09-01", "2021-10-01", "2021-11-01", "2021-12-01", "2022-01-01", "2022-02-01", "2022-03-01")), labels = c("Aug", "Sept", "Oct", "Nov", "Dec", "Jan", "Feb", "Mar"))
ggsave("figure1b.svg", g)
print(g)
```

# Uptake of first dose
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
kable(summary_factorlist_wt(z_df, "vacc_1_dose", c("age_range_group")))
```

# Uptake of second dose
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
summary_factorlist_wt(z_df, "vacc_2_dose", c("age_range_group"))
```

# Breakdowns of each age group
## 12 - 15 year olds
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE} 
z_df_12_15 = z_df %>% filter(age_range_group == "12 - 15") %>% mutate(age_gp = droplevels(age_gp))

# Have to relabel the age group after removing the unused levels
label(z_df_12_15$age_gp) = "Age"

summary_factorlist_wt(z_df_12_15, "vacc_1_dose", c("Sex", "simd2020_sc_quintile","age_gp"))
```

## 16 and 17 year olds
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
z_df_16_17 = z_df %>% filter(age_range_group == "16 - 17") %>% mutate(age_gp = droplevels(age_gp))

# Have to relabel the age group after removing the unused levels
label(z_df_16_17$age_gp) = "Age"

summary_factorlist_wt(z_df_16_17, "vacc_1_dose", c("Sex", "simd2020_sc_quintile","age_gp"))
```

# Uptake of second dose in each age group

## 12 - 15 year olds
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE} 
z_df_12_15 = z_df %>% filter(age_range_group == "12 - 15") %>% mutate(age_gp = droplevels(age_gp))

# Have to relabel the age group after removing the unused levels
label(z_df_12_15$age_gp) = "Age"

summary_factorlist_wt(z_df_12_15, "vacc_2_dose", c("Sex", "simd2020_sc_quintile","age_gp"))
```

## 16 and 17 year olds
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
z_df_16_17 = z_df %>% filter(age_range_group == "16 - 17") %>% mutate(age_gp = droplevels(age_gp))

# Have to relabel the age group after removing the unused levels
label(z_df_16_17$age_gp) = "Age"

summary_factorlist_wt(z_df_16_17, "vacc_2_dose", c("Sex", "simd2020_sc_quintile","age_gp"))
```

# Vulnerable children
## How many received a vaccine before the start of the program
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

qcovid_columns = grepl("Q_" ,names(z_df_vulnerable))
qcovid_columns_names = names(z_df_vulnerable)[qcovid_columns]

# Remove BMI cos it has lots of levels we don't care about
qcovid_columns_names = qcovid_columns_names[qcovid_columns_names != "Q_BMI"]
qcovid_columns[qcovid_columns_names == "Q_BMI"] = FALSE

# Create an extra column to hold if the person has a qcovid comorbidity
qcovid_comorbidity = apply(z_df_vulnerable[,qcovid_columns], 1, function(r) any(r == 1))

z_df_vulnerable[, qcovid_columns] = lapply(z_df_vulnerable[,qcovid_columns], factor)

z_df_vulnerable$qcovid_comorbidity = factor(qcovid_comorbidity)
qcovid_columns_names = c(qcovid_columns_names, "qcovid_comorbidity")

print(sum(z_df_vulnerable$eave_weight))
kable(summary_factorlist_wt(z_df_vulnerable, "Value", c("Sex", "simd2020_sc_quintile","age_range_group", "vacc_2_dose", "vacc_type", "qcovid_comorbidity"))) %>% kable_styling(full_width = F)
```

## How many of these children have some QCOVID comorbidity?
```{r echo = FALSE, message = FALSE, paged.print=FALSE}

kable(summary_factorlist_wt(z_df_vulnerable, "Value", qcovid_columns_names)) %>% kable_styling(full_width = F) # Force it to print all rows
```

## Build full table
```{r echo = FALSE, message = FALSE, paged.print = FALSE}
build_igors_table = function(z_df) {
  columns = c("vacc_1_dose", "vacc_2_dose")
  column_labels = c("1st Dose", "2nd Dose")
  z_table_overall = list()
  
  total_pop = sum(z_df$eave_weight)
  
  for (i in 1:length(columns)) {
    col = columns[i]
    z_table =  
      z_df %>% filter(age_range_group == "16 - 17") %>% filter(Sex == "M") %>%
      group_by(!!sym(col)) %>% summarise(n = sum(eave_weight)) %>% mutate(percentage = n/sum(n) * 100) %>% rename("M 16 - 17" = n, dose = !!sym(col), "M 16 - 17 %" = percentage)
    z_table = z_table %>% add_column( 
      z_df %>% filter(age_range_group == "16 - 17") %>% filter(Sex == "F") %>%
      group_by(!!sym(col)) %>% summarise(n = sum(eave_weight)) %>%  mutate(percentage = n/sum(n) * 100) %>% rename("F 16 - 17" = n, dose = !!sym(col), "F 16 - 17 %" = percentage) %>% select("F 16 - 17", "F 16 - 17 %"))
    z_table = z_table %>% add_column( 
      z_df %>% filter(age_range_group == "12 - 15") %>% filter(Sex == "M") %>%
      group_by(!!sym(col)) %>% summarise(n = sum(eave_weight)) %>%  mutate(percentage = n/sum(n) * 100) %>% rename("M 12 - 15" = n, dose = !!sym(col), "M 12 - 15 %" = percentage) %>% select("M 12 - 15", "M 12 - 15 %"))
    z_table = z_table %>% add_column( 
      z_df %>% filter(age_range_group == "12 - 15") %>% filter(Sex == "F") %>%
      group_by(!!sym(col)) %>% summarise(n = sum(eave_weight)) %>%  mutate(percentage = n/sum(n) * 100) %>% rename("F 12 - 15" = n, dose = !!sym(col), "F 12 - 15 %" = percentage) %>% select("F 12 - 15", "F 12 - 15 %"))
    z_table = z_table %>% add_column(
      z_df %>% group_by(!!sym(col)) %>% summarise(n = sum(eave_weight)) %>% mutate(percentage = n/total_pop * 100) %>% rename("Total" = n, dose = !!sym(col), "Total %" = percentage) %>% select("Total", "Total %"))
    z_table$label = column_labels[i]
    z_table_overall[[i]] = z_table
  }
  
  # Set up the final row which contains the total of each demographic category
  z_table =  
      z_df %>% filter(age_range_group == "16 - 17") %>% filter(Sex == "M") %>% summarise(n = sum(eave_weight)) %>% 
      mutate(percentage = n / total_pop * 100) %>% 
      rename("M 16 - 17" = n, "M 16 - 17 %" = percentage)
  
  z_table =  z_table %>% add_column(
      z_df %>% filter(age_range_group == "16 - 17") %>% filter(Sex == "F") %>% summarise(n = sum(eave_weight)) %>%
        rename("F 16 - 17" = n))
  
  z_table =  z_table %>% add_column(
      z_df %>% filter(age_range_group == "12 - 15") %>% filter(Sex == "M") %>% summarise(n = sum(eave_weight)) %>%
        rename("M 12 - 15" = n))
  
  z_table =  z_table %>% add_column(
      z_df %>% filter(age_range_group == "12 - 15") %>% filter(Sex == "F") %>% summarise(n = sum(eave_weight)) %>%
        rename("F 12 - 15" = n))

  
  z_table =  z_table %>% add_column(label = "Total")
  z_table =  z_table %>% add_column(
    z_df %>% summarise(n = sum(eave_weight)) %>% rename("Total" = n)  
  )
  z_table =  z_table %>% add_column(
    dose = "Any"
  )
  
  
  z_table_output = z_table_overall[[1]]
  z_table_output = z_table_output %>% add_row(z_table_overall[[2]]) %>% add_row(z_table) %>% relocate(label)
  
  # Now make it look nice
  # Percentages to 3 s.f.
  z_table_output = z_table_output %>% mutate(across(c("F 12 - 15 %", "M 12 - 15 %", "F 16 - 17 %", "M 16 - 17 %", "Total %"), ~formatC(round(.,1), format = "f", big.mark = ",", drop0trailing = TRUE)))
  
  # Numbers to integers
  z_table_output = z_table_output %>% mutate_if(is.numeric, ~formatC(round(.,0), format = "f", big.mark = ",", drop0trailing = TRUE))
  return(z_table_output)
}

z_table_output = build_igors_table(z_df)

kable(z_table_output) %>% kable_styling(full_width = F)
```
# Table for vulnerable population
## (Vacinated before the official program starts)
```{r echo = FALSE, message = FALSE, paged.print=FALSE}
z_table_output = build_igors_table(z_df_vulnerable)
kable(z_table_output) %>% kable_styling(full_width = F)
```

# Hospitalisations in cohort

```{r echo = FALSE, message = FALSE, paged.print=FALSE}
z_hosp = z_df %>% filter(!is.na(z_df$covid_hosp_date)) %>%
  filter(!is.na(flag_covid_symptomatic) & flag_covid_symptomatic == 1)
print(nrow(z_hosp))
print(summary_factorlist_wt(z_hosp, "Value", c("Sex", "simd2020_sc_quintile","age_range_group", "vacc_1_dose", "vacc_2_dose", "vacc_3_dose", "vacc_type", "vacc_type_2")), n=1000)
```