---
title: "Full Model - Covid-19 vaccine waning EAVE Cohort - VE relative to unvaccinated - TND in CHILDREN 12-17"
author: "Chris Robertson, Tristan Millington, Aziz Sheikh"
date: ' `r format(Sys.Date(), "%d %B %Y")` '
output: html_document
---

```{r setup, include=FALSE,echo = FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, error=FALSE)

# 01 Setup ####
#Libraries
library(tidyverse)
library(survival)
library(gridExtra)
library(ggplot2)
#library(htmltools)
#Load data

Location <- "/conf/"  # Server
#Location <- "//isdsf00d03/"  # Desktop
project_path <- paste0(Location,"EAVE/GPanalysis/progs/TM/vaccine_uptake_and_effectiveness_in_children")

source(paste0(project_path,"/00_Functions.R"))

#df_cc <- readRDS(paste0(project_path,"/output/temp/df_cc_pos_test.RDS")) %>% 
#  mutate(age_gp = factor(ageYear) )

```


# Number of tests and sgene status
```{r, results='asis', include=TRUE}

z_df_tests = df_s_gene
z_df_tests$t = z_df_tests$event_date - a_begin_16_17

number_tests = z_df_tests %>% filter(event == 1) %>%
                 dplyr::count(t) %>% 
                mutate(date = t + a_begin_16_17) 

number_s_gene_missing = z_df_tests %>% filter(!is.na(sgene_classification) & event == 1) %>% 
                   dplyr::count(t) %>% 
                mutate(date = t + a_begin_16_17) 

g = ggplot() + 
  geom_line(number_tests, mapping=aes(x=date, y=n), color="blue") + 
  geom_line(number_s_gene_missing, mapping=aes(x = date, y = n), color="red") + 
  xlab("Date") + ylab("Number of tests") + scale_x_date(breaks="1 month", date_labels="%b %Y") +
  geom_vline(xintercept = as.Date("2021-11-01")) + geom_vline(xintercept = as.Date("2022-01-15")) + theme_bw()
#plot(number_s_gene_missing$date,number_s_gene_missing$n, col='red', axes = TRUE, xlab = "Month and Year", ylab = "Number of #tests", xlim=c(a_begin_16_17, a_end), ylim=c(0, max(number_tests$n)))
#points(number_tests$date ,number_tests$n, col="blue")
print(g)
```

# Fraction of tests missing s gene status

```{r, results='asis', include=TRUE}

z_df_tests = df_s_gene
z_df_tests$t = z_df_tests$event_date - a_begin_16_17

number_tests = z_df_tests %>% filter(event == 1) %>%
                 dplyr::count(t) %>% 
                mutate(date = t + a_begin_16_17) 

number_s_gene_missing = z_df_tests %>% filter(is.na(sgene_classification) & event == 1) %>% 
                   dplyr::count(t) %>% 
                mutate(date = t + a_begin_16_17) 

z = number_tests %>% rename(n_tests = n) %>% left_join(number_s_gene_missing, by="date") %>% rename(n_sgene_missing = n)

z[is.na(z$n_sgene_missing),]$n_sgene_missing = 0

z$frac_missing = z$n_sgene_missing / z$n_tests

g = ggplot() + geom_line(z, mapping=aes(x=date, y=frac_missing), color="blue") + xlab("Date") + 
  ylab("Fraction of tests missing an sgene status") + geom_vline(xintercept = as.Date("2021-11-01")) +       
  geom_vline(xintercept = as.Date("2022-01-15")) + scale_x_date(breaks="1 month", date_labels="%b %Y") + theme_bw()
print(g)
```

# 16 - 17 year olds

##Pfizer Vaccine for dose 1 and 2 
###Risk Ratios

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
options(knitr.kable.NA = '')

z_df <- df_cc_16_17 %>% filter(vacc_type %in% c("uv", "PB"))
    
eqn = as.formula(paste("event"," ~ strata(EAVE_LINKNO_pos) + vs + ",
            paste(variables_hosp, collapse= " + ")))

ret = run_model(eqn, z_df, "event")

z_g = ret$z_g
z3 = ret$z3
z1 = ret$z1

z_g_2 = fun_plot_tnd_cc(z1, "", title="16 - 17 Years - All")
print(z_g_2)
```

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve(z3, "")
print(z_g_3)

```

###Vaccine Effects

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}

z_tab <- kableExtra::kbl(z3, 
                         caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1),
                         col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL"),
                         format = "pipe") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left") %>%
  kableExtra::column_spec(1:6, width="5em") %>% 
  #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
  #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))

print(z_tab)

```

##Pfizer Vaccine for dose 1 and 2 S Positive (Delta infections) 
###Risk Ratios

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
options(knitr.kable.NA = '')

z_df <- df_cc_16_17 %>% filter(vacc_type %in% c("uv", "PB"))

# Remove any later vaccine statuses - they just mess up the figures and don't contribute to any events
z_df = z_df %>% filter(!(vs == "v2_10:13" | vs == "v2_14+"))
z_df$vs = droplevels(z_df$vs)
z_df$vs = fct_recode(z_df$vs, "v2_6+" = "v2_6:9")
#z_df_cc$vs = factor(z_df_cc$vs, levels = c("uv", "v1_0:1", "v1_2:5", "v1_6:9", "v1_10:13", "v1_14:17", "v1_18+", "v2_0:1", "v2_2:5", "v2_6+"))

eqn = as.formula(paste("event_s_pos"," ~ strata(EAVE_LINKNO_pos) + vs + ",
            paste(variables_hosp, collapse= " + ")))
              
ret = run_model(eqn, z_df, "event_s_pos")

z_g = ret$z_g
z3 = ret$z3
z1 = ret$z1

z3_delta = z3

z_g_2 = fun_plot_tnd_cc(z1, "", title="16 - 17 years, Delta")
print(z_g_2)
ggsave("figure2a.svg", z_g_2)
```

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve(z3, "")
print(z_g_3)

```

###Vaccine Effects

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}

z_tab <- kableExtra::kbl(z3, 
                         caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1),
                         col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL"),
                         format = "pipe") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left") %>%
  kableExtra::column_spec(1:6, width="5em") %>% 
  #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
  #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))

print(z_tab)

```

##Pfizer Vaccine for dose 1 and 2 S Negative (Omicron infections) 
### Risk Ratios
```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
options(knitr.kable.NA = '')

z_df <- df_cc_16_17 %>% filter(vacc_type %in% c("uv", "PB"))

eqn = as.formula(paste("event_s_neg"," ~ strata(EAVE_LINKNO_pos) + vs + ",
            paste(variables_hosp, collapse= " + ")))
   
ret = run_model(eqn, z_df, "event_s_neg")

z_g = ret$z_g
z3 = ret$z3
z1 = ret$z1

z3_omicron = z3

z_g_2 = fun_plot_tnd_cc(z1, "", title="16 - 17 years, Omicron")
print(z_g_2)
ggsave("figure2b.svg", z_g_2)
```

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve(z3, "")
print(z_g_3)

```
###Vaccine Effects

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}

z_tab <- kableExtra::kbl(z3, 
                         caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1),
                         col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL"),
                         format = "pipe") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left") %>%
  kableExtra::column_spec(1:6, width="5em") %>% 
  #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
  #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))

print(z_tab)

```

## VE for both
```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve_both_variants(z3_delta, z3_omicron, "")
print(z_g_3)
```

## Producing the table for the paper
```{r, results='asis', include=TRUE, fig.width=12, fig.height=6}
z3_delta = z3_delta %>% mutate(events_delta = R, ve_delta = ve, lcl_delta = lcl, ucl_delta = ucl) %>%
 select(vs, N, events_delta, ve_delta, lcl_delta, ucl_delta)

# A hack to align the columns 
z3_delta = z3_delta %>% add_row(vs="v2_10:13", N=0, events_delta=0, ve_delta=0, lcl_delta=0, ucl_delta=0)
z3_delta = z3_delta %>% add_row(vs="v2_14+", N=0, events_delta=0, ve_delta=0, lcl_delta=0, ucl_delta=0)

z3_omicron = z3_omicron %>% mutate(events_omicron = R, ve_omicron = ve, lcl_omicron = lcl, ucl_omicron = ucl) %>%
 select(N, events_omicron, ve_omicron, lcl_omicron, ucl_omicron)

# levels = c("uv", "v1_0:1", "v1_2:5", "v1_6:9", , "v1_14:17", "v1_18+", "v2_0:1", "v2_2:5", "v2_6:9", )


z_combined = z3_delta %>% bind_cols(z3_omicron)
 
z_tab <- kableExtra::kbl(z_combined, 
                          caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1, 0, 0, 1, 1, 1),
                          col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL", "N", "Events", "VE", "LCL", "UCL"),
                          format = "pipe") %>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left")# %>%
   #kableExtra::column_spec(1:6, width="5em") %>% 
   #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
   #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))
# 
 print(z_tab)
```


#12 - 15 year olds
# Max Model

##Pfizer Vaccine for dose 1 and 2 
###Risk Ratios

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
options(knitr.kable.NA = '')

z_df <- df_cc_12_15 %>% filter(vacc_type %in% c("uv", "PB"))

eqn = as.formula(paste("event"," ~ strata(EAVE_LINKNO_pos) + vs + ",
            paste(variables_hosp, collapse= " + ")))

ret = run_model(eqn, z_df, "event")

z_g = ret$z_g
z3 = ret$z3
z1 = ret$z1

z_g_2 = fun_plot_tnd_cc(z1, "")
print(z_g_2)
ggsave("figure2c.svg", z_g_2)
```

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve(z3, "")
print(z_g_3)

```

###Vaccine Effects

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}

z_tab <- kableExtra::kbl(z3, 
                         caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1),
                         col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL"),
                         format = "pipe") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left") %>%
  kableExtra::column_spec(1:6, width="5em") %>% 
  #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
  #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))

print(z_tab)

```

##Pfizer Vaccine for dose 1 and 2 S Positive (Delta infections) 
###Risk Ratios

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
options(knitr.kable.NA = '')

z_df <- df_cc_12_15 %>% filter(vacc_type %in% c("uv", "PB"))

# Remove any later vaccine statuses - they just mess up the figures and don't contribute to any events
z_df = z_df %>% filter(!(vs == "v2_10:13" | vs == "v2_14+"))
z_df$vs = droplevels(z_df$vs)
z_df$vs = fct_recode(z_df$vs, "v2_6+" = "v2_6:9")
eqn = as.formula(paste("event_s_pos"," ~ strata(EAVE_LINKNO_pos) + vs + ",
            paste(variables_hosp, collapse= " + ")))
              
ret = run_model(eqn, z_df, "event_s_pos")

z_g = ret$z_g
z3 = ret$z3
z1 = ret$z1
z3_delta = z3
z_g_2 = fun_plot_tnd_cc(z1, "", title="12 - 15 years, Delta")
print(z_g_2)
ggsave("figure2d.svg", z_g_2)

```

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve(z3, "")
print(z_g_3)

```

###Vaccine Effects

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}

z_tab <- kableExtra::kbl(z3, 
                         caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1),
                         col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL"),
                         format = "pipe") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left") %>%
  kableExtra::column_spec(1:6, width="5em") %>% 
  #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
  #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))

print(z_tab)

```

##Pfizer Vaccine for dose 1 and 2 S Negative (Omicron infections) 
### Risk Ratios
```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
options(knitr.kable.NA = '')

z_df <- df_cc_12_15 %>% filter(vacc_type %in% c("uv", "PB"))

eqn = as.formula(paste("event_s_neg"," ~ strata(EAVE_LINKNO_pos) + vs + ",
            paste(variables_hosp, collapse= " + ")))
   
z <- clogit(eqn, data=z_df, method="efron")

ret = run_model(eqn, z_df, "event_s_neg")

z_g = ret$z_g
z3 = ret$z3
z1 = ret$z1
z3_omicron = z3
z_g_2 = fun_plot_tnd_cc(z1, "", title="12 - 15 years, Omicron")
print(z_g_2)
```

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}
z_g_3 = fun_plot_tnd_ve(z3, "")
print(z_g_3)

```
###Vaccine Effects

```{r,  results='asis', include=TRUE, fig.width=12, fig.height=6}

z_tab <- kableExtra::kbl(z3, 
                         caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1),
                         col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL"),
                         format = "pipe") %>%
  kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left") %>%
  kableExtra::column_spec(1:6, width="5em") %>% 
  #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
  #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))

print(z_tab)

```

## Producing the table for the paper
```{r, results='asis', include=TRUE, fig.width=12, fig.height=6}
z3_delta = z3_delta %>% mutate(events_delta = R, ve_delta = ve, lcl_delta = lcl, ucl_delta = ucl) %>%
 select(vs, N, events_delta, ve_delta, lcl_delta, ucl_delta)

# A hack to align the columns 
z3_delta = z3_delta %>% add_row(vs="v2_10:13", N=0, events_delta=0, ve_delta=0, lcl_delta=0, ucl_delta=0)
z3_delta = z3_delta %>% add_row(vs="v2_14+", N=0, events_delta=0, ve_delta=0, lcl_delta=0, ucl_delta=0)

z3_omicron = z3_omicron %>% mutate(events_omicron = R, ve_omicron = ve, lcl_omicron = lcl, ucl_omicron = ucl) %>%
 select(N, events_omicron, ve_omicron, lcl_omicron, ucl_omicron)

# levels = c("uv", "v1_0:1", "v1_2:5", "v1_6:9", , "v1_14:17", "v1_18+", "v2_0:1", "v2_2:5", "v2_6:9", )


z_combined = z3_delta %>% bind_cols(z3_omicron)
 
z_tab <- kableExtra::kbl(z_combined, 
                          caption = "Numbers and Vaccine Effects", digits=c(NA,0,0,1,1,1, 0, 0, 1, 1, 1),
                          col.names = c("Vaccine Status","N","Events", "VE", "LCL","UCL", "N", "Events", "VE", "LCL", "UCL"),
                          format = "pipe") %>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria", position = "left")# %>%
   #kableExtra::column_spec(1:6, width="5em") %>% 
   #kableExtra::column_spec(c(4,7,10), width="5em") %>% 
   #kableExtra::add_header_above(c(" " = 4, "Rate Ratio" = 3, "Vaccine Effect" = 3))
# 
 print(z_tab)
```



